\subsection{Case Study A: Financial Institution}

\subsubsection{Enterprise Context and Objectives}
This case examines a regulated financial institution exploring permissioned blockchain for interbank settlement and asset tokenization. Objectives include operational resilience, compliance alignment, and quantifiable ROI through process automation and reduced reconciliation overhead.

\subsubsection{System Architecture and Integration Touchpoints}
Summarize core systems (core banking, KYC/AML, custody/HSM, SIEM/SOC, API gateways) and blockchain platform components (consortium network, consensus mechanism, node topology, key management).

\subsubsection{Scope and Assumptions}
Define boundaries (pilot vs. production), data classification, participating entities, regulatory jurisdictions, and third-party dependencies.

\subsubsection{B-SAFE Checklist Application}
The following table captures checklist outcomes at the capability level. Status reflects current readiness; Score is an ordinal readiness measure (0–3); Gaps capture blockers; Owner is accountable function.

\begin{table}[H]
\centering
\caption{Checklist outcomes (Financial Institution)}
\begin{tabularx}{0.98\linewidth}{l l c X l}
\toprule
\textbf{Domain} & \textbf{Capability} & \textbf{Score} & \textbf{Gap/Action} & \textbf{Owner} \\
\midrule
Business & Strategic Alignment &  &  & CTO Office \\
Business & ROI Model &  &  & Finance \\
Technical & Integration Readiness &  &  & Platform Eng \\
Technical & Infrastructure Baseline &  &  & SRE \\
Human & Skills \& Training &  &  & HR/Tech L\'ead \\
Architecture & Platform Selection &  &  & Architecture Board \\
Security & Key Management (HSM) &  &  & Security Eng \\
Security & Smart Contract Audit &  &  & AppSec \\
Compliance & Regulatory Mapping &  &  & Compliance \\
Operations & Incident Response &  &  & SOC \\
Deployment & Pilot Plan &  &  & PMO \\
\bottomrule
\end{tabularx}
\label{tab:fi_checklist}
\end{table}

\subsubsection{Risk and Success Metrics}
Define leading/lagging indicators and acceptance criteria.

\begin{table}[H]
\centering
\caption{Risk and success metrics}
\begin{tabularx}{0.98\linewidth}{l X X l}
\toprule
\textbf{Metric} & \textbf{Baseline} & \textbf{Target/Threshold} & \textbf{Data Source} \\
\midrule
Key Compromise Probability &  &  & HSM audit logs \\
Settlement Latency (p95) &  &  & Monitoring (APM) \\
Change Failure Rate &  &  & SDLC metrics \\
Incident MTTR &  &  & SOC tickets \\
Compliance Exceptions &  &  & GRC tool \\
\bottomrule
\end{tabularx}
\label{tab:fi_metrics}
\end{table}

\subsubsection{Findings and Recommendations}
Provide prioritized remediation actions with rationale, dependencies, and expected impact.

\subsubsection{Deployment and Change Management Plan}
Outline phased rollout, environment promotion strategy, and rollback/kill-switch design.

\subsubsection{Residual Risk and Next Steps}
Document residual risks, sign-offs required, and plan for continuous monitoring and periodic reassessment.


