\subsection{Case Study B: Supply Chain Pilot}

\subsubsection{Enterprise Context and Objectives}
This case examines a multinational supply chain pilot for provenance tracking and compliance attestations across suppliers, logistics providers, and retailers. Objectives include traceability, data integrity, and operational interoperability.

\subsubsection{System Architecture and Integration Touchpoints}
Summarize ERP/WMS/TMS integration, IoT/edge data capture, identity/PKI, and blockchain platform components.

\subsubsection{Scope and Assumptions}
Define pilot lanes, product categories, data sharing agreements, and privacy constraints (PII/PCI/GDPR).

\subsubsection{B-SAFE Checklist Application}
Checklist outcomes are captured below for supply chain specifics (partner onboarding, data schemas, offline security, and API posture).

\begin{table}[H]
\centering
\caption{Checklist outcomes (Supply Chain Pilot)}
\begin{tabularx}{0.98\linewidth}{l l c X l}
\toprule
\textbf{Domain} & \textbf{Capability} & \textbf{Score} & \textbf{Gap/Action} & \textbf{Owner} \\
\midrule
Business & Partner Incentive Design &  &  & Program Mgmt \\
Technical & ERP/IoT Integration &  &  & Platform Eng \\
Human & Vendor Management &  &  & Procurement \\
Architecture & Consensus/Topology &  &  & Architecture \\
Security & API Security (Zero Trust) &  &  & Security Eng \\
Security & Data Privacy Controls &  &  & DPO \\
Compliance & Cross-border Data &  &  & Legal \\
Operations & Incident Playbooks &  &  & SOC \\
Deployment & Pilot Rollout Plan &  &  & PMO \\
\bottomrule
\end{tabularx}
\label{tab:sc_checklist}
\end{table}

\subsubsection{Risk and Success Metrics}
\begin{table}[H]
\centering
\caption{Risk and success metrics}
\begin{tabularx}{0.98\linewidth}{l X X l}
\toprule
\textbf{Metric} & \textbf{Baseline} & \textbf{Target/Threshold} & \textbf{Data Source} \\
\midrule
Data Integrity Violations &  &  & Audit logs \\
API Abuse Incidents &  &  & WAF/IDS \\
Partner Onboarding Time &  &  & PMO trackers \\
Uptime SLO Compliance &  &  & SRE dashboards \\
Privacy Violations &  &  & DLP reports \\
\bottomrule
\end{tabularx}
\label{tab:sc_metrics}
\end{table}

\subsubsection{Findings and Recommendations}
Provide prioritized steps and trade-offs for partner onboarding, data standards, and security posture.

\subsubsection{Deployment and Change Management Plan}
Outline pilot cadence, KPIs to graduate to production, and rollback criteria.

\subsubsection{Residual Risk and Next Steps}
Document residual risks, governance updates, and continuous improvement loop.


