\section{Literature Review}
This section reviews existing literature on the metaverse, focusing on virtual economies, property valuation, and market dynamics. It highlights the significance of blockchain technology in ensuring transparency and security in virtual transactions. The review also discusses the role of NFTs in representing ownership of virtual assets and the implications of play-to-earn models on user engagement and economic activity within the metaverse.
The literature indicates a growing interest in the economic aspects of virtual worlds, with studies examining the impact of digital identities and decentralized platforms on user interactions and property values. Additionally, the review identifies gaps in current research, particularly in the areas of data analytics and predictive modeling for virtual real estate markets. This study aims to address these gaps by providing a comprehensive analysis of Decentraland's real estate market, utilizing advanced data collection and analytical techniques to derive meaningful insights into virtual property dynamics.
The review also emphasizes the need for interdisciplinary approaches, combining insights from economics, computer science, and sociology to better understand the complexities of virtual economies. By integrating these perspectives, the study seeks to contribute to a more nuanced understanding of how virtual properties are valued and traded, and how these dynamics may evolve as the metaverse continues to develop.